Abstractions for Multi-Sorted Substitutions

### 2024-03-14 paper/paper.tex
Update.

  \subsection{Type Contexts}
  \begin{figure}
    \centering
    % \LibCode\KContextHelper
    \begin{minipage}{1.0\linewidth}
      \begin{minipage}{0.57\linewidth}
        \LibCode\KContexts
        \LibCode\KContextLookupI
        \LibCode\KVariableTyping
      \end{minipage}
      \begin{minipage}{0.43\linewidth}
        \LibCode\KContextExt
        \LibCode\KContextLookupII
        \vspace{10.1mm}
      \end{minipage}
    \end{minipage}
    \caption{Type Contexts}
    \label{fig:type-contexts}
  \end{figure}
  Equipped with a notion of types, we are ready to define type contexts as shown
  in Figure~\ref{fig:type-contexts}.
  The type \ACode{\ADef{Ctx} S} describes type contexts with bindings for variables from \ACode{S}
  as functions that map variables to types of the same sort.
  As we want our framework to support dependent types, we allow a type
  in the context to use all variables bound previously in the context.
  This is achieved with \ACode{\ADef{drop-∈} x S}, which cuts off all
  sorts from \ACode{S} that are at smaller or equal positions than a variable \ACode{x}.
  The \ACode{\ADef{\_∷ᵗ\_}} function extends a context with a new binding.
  The \ACode{\ADef{lookup}} function looks up the type of a variable in a context
  and weakens it appropriately.
  Finally, a variable typing \ACode{Γ \ADef{∋} x \ADef{∶} t} is defined in terms of \ACode{\ADef{lookup}}.

>>>>

  \subsection{Type Contexts}
  \begin{figure}
    \centering
    % \LibCode\KContextHelper
    \begin{minipage}{1.0\linewidth}
      \begin{minipage}{0.57\linewidth}
        \LibCode\KContexts
        \LibCode\KContextLookupI
        \LibCode\KVariableTyping
      \end{minipage}
      \begin{minipage}{0.43\linewidth}
        \LibCode\KContextExt
        \LibCode\KContextLookupII
        \vspace{10.1mm}
      \end{minipage}
    \end{minipage}
    \caption{Type Contexts}
    \label{fig:type-contexts}
  \end{figure}
  Equipped with a notion of types, we are ready to define type contexts as shown
  in Figure~\ref{fig:type-contexts}.
  \ACode{\ADef{Ctx} S} describes type contexts with bindings for variables from \ACode{S}
  as functions that map variables to types of the same sort.
  As we want our framework to support dependent types, we allow a type
  in the context to use all variables bound previously in the context.
  This is achieved with \ACode{\ADef{drop-∈} x S}, which cuts off all
  sorts from \ACode{S} that are at smaller or equal positions than a variable \ACode{x}.
  The \ACode{\ADef{\_∷ᵗ\_}} function extends a context with a new binding.
  The \ACode{\ADef{lookup}} function looks up the type of a variable in a context
  and weakens it appropriately.
  Finally, a variable typing \ACode{Γ \ADef{∋} x \ADef{∶} t} is defined in terms of \ACode{\ADef{lookup}}.
